\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}


\begin{document}

\noindent{\huge\textbf{Matthew Stobo}}
\vspace{0.8em}
\hrule
\vspace{0.4em}


\hfill 2A Software Engineering $\bullet$ 
mwstobo@gmail.com $\bullet$ (416) 527-3316

\hfill116 Albert Street, Stouffville, ON, L4A 1B1

\hfill https://github.com/mwstobo

\smallskip

\raggedright

\noindent{\large\emph{SKILLS/ABILITIES}}
\begin{itemize}
\parskip=0.1em
\item Highly proficient in Java, \CPP, C, Python and shell scripting (UNIX and Windows).  Experience with the object-oriented programming paradigm.
\item Familiar with PHP, HTML, CSS, Javascript, Perl and \LaTeX.  Maintained databases using MySQL, SQLite and Oracle relational database management systems.
\item Relevant experience with various web frameworks and developer tools such as Django, vim, git and Rational ClearCase.  Exposure to software development methods like Agile and Waterfall.
\item Experience setting up and running a web server using the LAMP (Linux, Apache, MySQL, PHP) paradigm.
\end{itemize}

\noindent{\large\emph{EXPERIENCE}}
\begin{itemize}
\parskip=0.1em
\item\textbf{Software Developer}, SAP AG, Waterloo, ON \hfill 2013
\begin{itemize*}
\item Developed the installer for the relational database product, Sybase IQ.  Added new features and fixed any bugs reported.
\item Explored beyond the scope of the installer by creating small tools to speed up development times.
\item Enhanced communication skills by attending weekly agile status meetings and presenting to coworkers.
\end{itemize*}
\item\textbf{Landscaper}, Omega Landscaping, Stouffville, ON \hfill 2010 - 2012
\begin{itemize*}
\item Accomplished all tasks with high efficiency and client satisfaction.
\item Communicated effectively with clients and colleagues to optimize workload.
\end{itemize*}
\item\textbf{Dota to SQLite}, Personal Project (source on GitHub) \hfill 2013
\begin{itemize*}
\item A Python script that accesses the Dota 2 API and stores information on matches played by a specified ID.
\item Makes an API call, parses the returned data and stores it in a local SQLite database.
\end{itemize*}
\item\textbf{Volunteer Program Leader}, Whitchurch-Stouffville Public Library \hfill 2009 - 2011
\begin{itemize*}
\item Organized and ran after-school chess programs for children.
\item Created a learning environment for children to have fun develop their mental skills.
\end{itemize*}
\end{itemize}

\noindent{\large\emph{EDUCATION}}
\begin{itemize}
\parskip=0.1em
\item\textbf{University of Waterloo}, Waterloo, ON \hfill 2012 - Present
\begin{itemize*}
\item Bachelor of Software Engineering (Candidate).
\end{itemize*}
\item\textbf{St. Brother Andre Catholic High School}, Markham, ON \hfill 2008 - 2012
\begin{itemize*}
\item Graduated in the Advanced Placement program with an average of 96\%.
\end{itemize*}
\end{itemize}

\noindent{\large\emph{AWARDS/DISTINCTIONS}}
\begin{itemize}
\parskip=0.1em
\item\textbf{University of Waterloo}, Waterloo, ON
\begin{itemize}
\item President's Scholarship of Distinction, 2012.  Awarded for an entrance average of 95\% or above.
\end{itemize}
\item\textbf{St. Brother Andre Catholic High School}, Markham, ON
\begin{itemize}
\item AP Exams, 2012.  5 on Calculus AB and 4 on Chemistry.
\item Principal's List, 2009-2012.  Received and award each year for being one of the top ten students.
\end{itemize}
\end{itemize}

\noindent{\large\emph{ACTIVITIES/INTERESTS}}
\begin{itemize}
\parskip=0.1em
\item Recreational programming.  Create many small personal projects in order to learn new techniques and languages.
\item Active participant in the video game speed running community.  Hunting for game-breaking bugs and glitches that allow for faster completion of a game.
\item Playing classical piano.  Received certification from the Royal Conservatory of Music.
\item Team sports such as hockey and baseball, as well as passion for the art of film.
\end{itemize}

\end{document}

