\documentclass[11pt,letterpaper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage[scale=0.84]{geometry}

\name{Matthew}{Stobo}
\address{21 Roslin Avenue South}{Waterloo, ON}
\phone{(416)~527~3316}
\email{mwstobo@gmail.com}
\social[github]{mwstobo}
\social[linkedin]{mwstobo}
\extrainfo{4A Software Engineering\quad\textbullet\quad20480115}

\begin{document}

\makecvtitle
\kern-3em

\section{Experience}
\cventry{Winter 2016}{Software Engineer}{Coursera}{Mountain View, CA}{}{
	Took on various roles, including project lead, to improve Coursera's online learning platform. \vspace{0.5em}
    \begin{itemize}
	% Search
	\item Headed a project to increase user productivity by overhauling the course forums search engine.
	% Programming assignments
	\item Expedited the course creation processes by augmenting error reporting for automated assignment graders.
	% Facl
	\item Advanced new forms of online education by helping develop a mentor-led learning system.
	\end{itemize}
}
\cventry{Summer 2015}{Software Developer}{Wave Accounting}{Toronto, ON}{}{
	Developed the payments platform powering thousands of small businesses.\vspace{0.5em}
	\begin{itemize}
	% ACH
	\item Expanded our payments platform to Canadian businesses by helping create a new direct deposit platform.
	% Siren
	\item Enabled the platform to grow by adding many missing features to our in-house risk analysis tools.
	% RFCs
	\item Raised productivity by automatically creating a risk assessment when users change personal information.
	\end{itemize}
}
\cventry{Fall 2014}{Server Developer}{Enflick Inc.}{Waterloo, ON}{}{
	Developed the API powering the TextNow Wireless messaging and calling service.\vspace{0.5em}
	\begin{itemize}
	% Inventory refactor
	\item Greatly increased productivity by refactoring how returns are managed in the internal inventory system.
	% Sprint refactor
	\item Enabled customers to port their personal phones to TextNow by creating a proxy to Sprint's external API.
	% Windows IAP
	\item Allowed users to make purchases from Windows Phone by writing server side validation for receipts.
	\end{itemize}
}
\cventry{Winter 2014}{Web Developer}{Influitive Corporation}{Toronto, ON}{}{
	Maintained and created features for an advocate marketing platform running Ruby on Rails.\vspace{0.5em}
	\begin{itemize}
	\item Increased user engagement by helping to implement a community forum containing comments and likes.
	\item Improved developer efficiency by refactoring and implementing tests for old code.
	\end{itemize}
}
\cventry{Summer 2013}{Software Developer}{SAP AG}{Waterloo, ON}{}{
	Continued development of the multiplatform installer for the Sybase IQ database software.\vspace{0.5em}
	\begin{itemize}	
	\item Streamlined the build process by adding new command line features and removing compile time warnings.
	\item Improved software stability by upgrading the installer back end to the newest version.
	\end{itemize}
}

\section{Skills}
\cvitem{Languages}{(\textbf{Workterm} Scala, Python, Ruby, JavaScript, PHP, CSS, Shell) (\textbf{School} C++, C, Java, \LaTeX)}
\cvitem{Frameworks}{(\textbf{Workterm} Naptime (Play), Django, Angular, Rails, Sinatra) (\textbf{Personal} React, Flask)}
\cvitem{Technologies}{(\textbf{Workterm} Solr, Cassandra, Kafka, Postgres, Git, vim, Redis, MySQL) (\textbf{Personal} RabbitMQ)}

\section{Education}
\cventry{2012--Present}{Bachelor of Software Engineering}{University of Waterloo}{Waterloo, ON}{}{Candidate, Expected 2017}

\section{Interests}
\cvitem{Speedrunning}{Hunting for game-breaking bugs and glitches that allow for insanely fast completion of a video game is what makes speedrunning so enjoyable to me.}
\cvitem{Board Games}{I enjoy playing many different speciality board games, especially Dominion, Settlers of Catan and Avalon.  They're even more fun when played during lunch hours!}
\cvitem{Reading}{I'm a big fan of fantasy novels. Right now I'm into Brandon Sanderson's Stormlight Archive while waiting for The Winds of Winter.}


\end{document}
